Abstractions for Multi-Sorted Substitutions

### 2023-08-30 paper/paper.tex
Update.

  In contrast we define structures similar to \ACode{\ACon{Kit}} and
  \ACode{\ACon{Traversal}}, which allows us to abstract over all four
  compositions and use the same trick as before to eliminate the
  dependencies.
  This has the benefit that a user of our library has to write less
  boilerplate, but more importantly it allows to prove lemmas about the
  composition of arbitrary maps, which enables us to later unify type
  preservation of all substitution and renaming operations into a single
  lemma.

@@

  \ExampleCode\KExFourComps
  \ExampleCode\KExTwoComps
  \ExampleCode\KComposition

>>>>

  In contrast we define structures similar to \ACode{\ACon{Kit}} and
  \ACode{\ACon{Traversal}}, which allows us to abstract over all four
  compositions and use the same trick as before to eliminate the
  dependencies.
  This has the benefit that a user of our library has to write less
  boilerplate, but more importantly it allows to prove lemmas about the
  composition of arbitrary maps, which enable us later to unify type
  preservation of all substitution and renaming operations into a single
  lemma.

  \subsection{An Examination of Composition}
  With the infrastructure we build in the previous sections, we can
  define the four compositions as followed:
  \ExampleCode\KExFourComps
  The definitions reveal an interesting asymetry, in the sense that
  the first argument of composition guides the implementation: if we
  compose a renaming with any map, then we first apply renaming to the
  the variable, which yields another variable, so we apply the second
  map to that \emph{variable}.
  However, if we compose a substitution with any map, then we first
  apply the substitution to that variable, which yields a term, so we
  need to apply the second map to that \emph{term}.

  With the machinery, we built so far, we can unify the first two and
  last two compositions as followed:
  \ExampleCode\KExTwoComps

  But to unify those two compositions, we need a new abstraction.

  \ExampleCode\KComposition

@@
